\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-08-31 manuscript/Rmd/draft.Rmd

@@

@@

>>>>

Women: lead and bouldering belong to the same component, the other is speed.

"overall ability"

"power"

@@

How each variable contributes to each principal component

```{r}
tidy(wq_pca, matrix = "loadings") %>%
  ggplot(aes(value, column)) +
  facet_wrap(~ PC) +
  geom_col()
```

@@

```{r}
tidy(mq_pca, matrix = "loadings") %>%
  ggplot(aes(value, column)) +
  facet_wrap(~ PC) +
  geom_col()
```

### 2021-08-31 manuscript/Rmd/draft.tex

@@

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-24-1}

@@

\caption{Men's Qualification PCA}\label{fig:unnamed-chunk-24}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-26}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2018 Asian Games}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5731 & 0.6760 & 0.6126 & 1.0000 & 0.5474 & 0.6878 & 0.7053\\
Speed & 0.5731 & 1.0000 & 0.3022 & 0.2174 & 0.5474 & 1.0000 & 0.2540 & 0.2947\\
Bouldering & 0.6760 & 0.3022 & 1.0000 & 0.6203 & 0.6878 & 0.2540 & 1.0000 & 0.6878\\
Lead & 0.6126 & 0.2174 & 0.6203 & 1.0000 & 0.7053 & 0.2947 & 0.6878 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-27}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2019 World Championships}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.2632 & 0.3684 & 0.3474 & 1.0000 & 0.2316 & 0.5013 & 0.2526\\
Speed & 0.2632 & 1.0000 & -0.0947 & -0.3263 & 0.2316 & 1.0000 & 0.0686 & -0.4526\\
Bouldering & 0.3684 & -0.0947 & 1.0000 & 0.2000 & 0.5013 & 0.0686 & 1.0000 & 0.2902\\
Lead & 0.3474 & -0.3263 & 0.2000 & 1.0000 & 0.2526 & -0.4526 & 0.2902 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-28}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 European Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.0947 & 0.3810 & 0.2632 & 1.0000 & 0.1847 & 0.5358 & 0.5368\\
Speed & 0.0947 & 1.0000 & -0.1587 & -0.4316 & 0.1847 & 1.0000 & -0.1915 & -0.0897\\
Bouldering & 0.3810 & -0.1587 & 1.0000 & 0.2751 & 0.5358 & -0.1915 & 1.0000 & 0.5040\\
Lead & 0.2632 & -0.4316 & 0.2751 & 1.0000 & 0.5368 & -0.0897 & 0.5040 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-29}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 Pan American Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5906 & 0.5556 & 0.6491 & 1.0000 & 0.5789 & 0.6140 & 0.5906\\
Speed & 0.5906 & 1.0000 & 0.2164 & 0.4035 & 0.5789 & 1.0000 & 0.2632 & 0.3099\\
Bouldering & 0.5556 & 0.2164 & 1.0000 & 0.2749 & 0.6140 & 0.2632 & 1.0000 & 0.3918\\
Lead & 0.6491 & 0.4035 & 0.2749 & 1.0000 & 0.5906 & 0.3099 & 0.3918 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

Women: lead and bouldering belong to the same component, the other is
speed.

``overall ability''

``power''

@@

How each variable contributes to each principal component

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-24-1} \end{center}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-25-1}

@@

\caption{Men's Qualification PCA}\label{fig:unnamed-chunk-25}
\end{figure}

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-26-1} \end{center}

@@

\caption{\label{tab:unnamed-chunk-28}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2018 Asian Games}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5731 & 0.6760 & 0.6126 & 1.0000 & 0.5474 & 0.6878 & 0.7053\\
Speed & 0.5731 & 1.0000 & 0.3022 & 0.2174 & 0.5474 & 1.0000 & 0.2540 & 0.2947\\
Bouldering & 0.6760 & 0.3022 & 1.0000 & 0.6203 & 0.6878 & 0.2540 & 1.0000 & 0.6878\\
Lead & 0.6126 & 0.2174 & 0.6203 & 1.0000 & 0.7053 & 0.2947 & 0.6878 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-29}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2019 World Championships}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.2632 & 0.3684 & 0.3474 & 1.0000 & 0.2316 & 0.5013 & 0.2526\\
Speed & 0.2632 & 1.0000 & -0.0947 & -0.3263 & 0.2316 & 1.0000 & 0.0686 & -0.4526\\
Bouldering & 0.3684 & -0.0947 & 1.0000 & 0.2000 & 0.5013 & 0.0686 & 1.0000 & 0.2902\\
Lead & 0.3474 & -0.3263 & 0.2000 & 1.0000 & 0.2526 & -0.4526 & 0.2902 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-30}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 European Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.0947 & 0.3810 & 0.2632 & 1.0000 & 0.1847 & 0.5358 & 0.5368\\
Speed & 0.0947 & 1.0000 & -0.1587 & -0.4316 & 0.1847 & 1.0000 & -0.1915 & -0.0897\\
Bouldering & 0.3810 & -0.1587 & 1.0000 & 0.2751 & 0.5358 & -0.1915 & 1.0000 & 0.5040\\
Lead & 0.2632 & -0.4316 & 0.2751 & 1.0000 & 0.5368 & -0.0897 & 0.5040 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-31}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 Pan American Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5906 & 0.5556 & 0.6491 & 1.0000 & 0.5789 & 0.6140 & 0.5906\\
Speed & 0.5906 & 1.0000 & 0.2164 & 0.4035 & 0.5789 & 1.0000 & 0.2632 & 0.3099\\
Bouldering & 0.5556 & 0.2164 & 1.0000 & 0.2749 & 0.6140 & 0.2632 & 1.0000 & 0.3918\\
Lead & 0.6491 & 0.4035 & 0.2749 & 1.0000 & 0.5906 & 0.3099 & 0.3918 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}
